The globular cluster system of the Auriga simulations

### 2020-04-11 response_to_referee.tex

\documentclass{article}

\begin{document}

\section*{Introduction}
We thank the referee for a thoughtful and elaborate report. We address the 
comments in sections with headings that match those of the referee report, 
starting with the following listing of our response to the first 2 paragraphs in 
the introduction.
\begin{enumerate}
\item We updated the abstract and conclusion to clarify that we meant to describe
what would be needed for the environmental dependence of the formation and disruption
of bound clusters for the Auriga simulations to be consistent with the observations,
rather than to argue that the Auriga simulations reflect these trends.
\item
We feel that our conclusion would be too strongly phrased if we would generalise 
our results obtained using the Auriga simulations to cosmological simulations 
in general. We find that age-selected stellar particles in the Auriga simulations 
do not reproduce key properties of observed GC systems in the Milky Way and M31.
However, our results might reflect characteristics that are specific to Auriga, 
e.g. that the galaxy formation model overmixes metals at early times. 
Therefore we did add a final bulletpoint to our conclusion to clarify the above, 
but we limit the scope to the Auriga simulations. Thanks for pointing this out!

Furthermore, we clarified in the manuscript that we investigate the metallicity
and galactocentric radius because these properties are available for the observed
GC systems and in the simulations.
% \item TODO: disussion of implications for wider context.
\end{enumerate}

@@

\section*{General comments about style}
\begin{itemize}
\item Numerical quantities are now described in arabic numbers instead of words.
\item We now first use the name of the physical quantities in the given example,
    followed by the symbolic representation.
\item The text has been updated to reduce the usage of parenthesis.
\item Colloquial expressions have been rephrased.
\item We replaced `Sec.' by `Section' to refer to sections in the present work.
Moreover, we changed `Sec.' to `section' to refer to a section in one of the references.
\item All acronyms are introduced the first time they appear in the text
(MW, M31, GC, GCS, YMC, ISM, SN, AGB, DM, and Au). The subset thereof that appears 
in the abstract is also introduced the first time it appears.
\item The colour palette has been updated to improve colourblind-friendliness.
\item We no longer use blue and red to prevent confusion because they are 
typically used for metal-poor and metal-rich populations.
\end{itemize}

\section*{Major comments and concerns}
\begin{itemize}
\item We updated the introduction to make it more clear why we consider the metallicity
and galactocentric radius in light of {\it in~situ} formation or accretion of GC
candidates.
\item We added section 5.3 to discuss how our results change of we adopt an age cut
of 8 or 6 Gyr.
\end{itemize}

\section*{Additional major comments}
\begin{itemize}
% \item TODO justify the modelling philosophy.
\item We added a section 5.3 to discuss how our results change if we adopt an
age cut of 8 or 6 Gyr instead of 10 Gyr.
\item We clarified that the number of observed GCs differs between Figure 1 and 
Figure 2 because the latter shows metallicities between -2.5 and 0, galactocentric 
radii between 1 and 250 kpc. Figure 1, on the other hand, shows the full range
of radii, and the top panel of Figure 3 shows the full range of metallicities.
\item We normalise the Auriga simulations by the virial radius of the
dark matter halo to compensate for scatter between different simulation runs. We
deliberately chose for $r_{vir}$ because there are several stellar length scales
that could be used (e.g. the effective radius of the bulge, the radial scalelength
or vertical scaleheight of the disk, the optical radius, the extent of the stellar 
halo, the half-mass stellar radius, etc). The simulations show a wide variety 
between properties of the Auriga galaxies with little correlation between these 
different stellar length scales. Therefore we could introduce unknown biases by 
normalising to any one of these options which is why we use the virial radius instead.
% \item TODO: ``Discussion on the implications for the formation and evolution of clusters
%    often feels a bit out of place and forced.''

@@

\end{itemize}

\section*{Comments for each section}
\subsection*{Introduction}
\begin{itemize}
\item We clarified that the blue and red GCs are observed to have different colour
distributions that may reflect a different metallicity distribution which is argued
to arise from two distinct formation channels. We briefly summarise that differences
between their properties include the metallicity and radial distributions, which
is why we investigate these properties in the Auriga simulations.
\item We removed the quoted sentence.
\end{itemize}

@@

\subsection*{Sect. 2 -}
\begin{itemize}
\item We added the halo mass range of the Auriga simulations.
\item The last paragraph should now make more sense after updating the introduction.
\end{itemize}

\subsection*{Sect. 3 -}
\begin{itemize}
\item We added references to section 3.3, 3.4, and 3.5 in the first paragraph of section 3.
\item Section 3.2 has been restructured.
\item We removed the standard error on the mean and replaced `dispersion' 
by `standard deviation' in section 3.3.
\item We added a sentence to clarify the last statement in section 3.4.
\end{itemize}

\subsection*{Sect. 4 -}
\begin{itemize}
\item We added the mean number of GC candidates compared to the mean number of
star particles in the Auriga L4 galaxies. In addition, Figure 3 now shows the 
number of star particles included in each subset.
\item We clarified at various places whether we mean the mean or median among
the simulations, or if we refer to the absolute value of one of the galaxies.
\item We added the suggestion in the 3rd paragraph of section 4.1.
\item Bimodality in GC systems is now discussed in the introduction.
\item Figure 4 - now has a vertical line to indicate the metallicity cut 
between metal-poor and metal-rich GC subpopulations in the Milky Way.
\item We added a sentence about the cluster formation efficiency model of 
Kruijssen (2012) in the last paragraph of section 4.1.
\item We now show the median instead of the mean for the galactocentric radius in
section 4.2 and Figure 6.
\item Figure 6: no changes were made for rescaling the galaxies (i.e. we still
use the virial radius)
\item Figure 5 and 7: shaded regions now show the 25-75th percentiles.
\item We added a brief discussion of Figure 8.
\item We clarified that we are referring to Figure 5 and Figure 7 for the claims about
the {\it in~situ} and accreted component in the third paragraph of section 4.3.
\item Figure 9: The values are removed from the masked upper right corner bins.
\item Figure 2,8,9: The values of the upper and right axes have been removed from
Figure 2 and 9 (observations) for clarity (rather than the suggestion to add 
axis labels and units). However, we did not mask these bins for Figure 8 (Auriga)
because it illustrates our finding that the simulations produce a considerable
amount of mass in GC candidates with low metallicities at large radii.
\end{itemize}

\subsection*{Sect. 5 -}
\begin{itemize}
\item We added references to Deason et al. (2015) and Conroy et al. (2019) in
the first paragraph of section 5.1.
\item We included a discussion of bimodality in metallicities in the introduction.
In addition to that, the results of Usher et al. (2012) ``imply that most early-type 
galaxies in the SLUGGS survey have bimodal metallicity as well as colour distributions'',
and ``Combined with previous studies, nine of 12 galaxies show evidence for bimodality
while in the remaining three galaxies bimodality cannot be ruled out.''. Our 
interpretation of this study seems to differ from that of the referee.
\item We still find that the accreted star particles are more metal-poor than 
those that have formed {\it in~situ} if we lower the age cut to 8 or 6 Gyr.
This has been added in section 5.3.
\item We removed the quoted sentence.
\item We clarified that our selection function is inconsistent with the definition
\item We clarified which which galaxy Brodie \& Strader provide the quoted number.
\item We clarified footnote 8.
of Kruijssen (2019) for {\it ex~situ} GC formation.
\end{itemize}

### 2020-04-11 AurigaGCS.tex
Version to send to Simon

\section{Introduction}
Globular star clusters (GC)s are old, bright, and ubiquitous. Various properties of
GC systems (GCS) show correlations with their host galaxies. GCSs are believed to
retain information about the galactic (gas) conditions at their times of formation.
Thus they could offer a unique insight into the (chemodynamical) evolution of their 
parent galaxies, if the formation and evolution of GCs- and GC systems themselves 
is adequately understood. However, despite decades of research (the extensive 
literature on GCs is summarised in several books and review articles, e.g.~\citealt{
1991ARA&A..29..543H, Harris2001, 2004Natur.427...31W, 2006ARA&A..44..193B, 
2012A&ARv..20...50G, 2014CQGra..31x4006K, 2018RSPSA.47470616F}), consensus on an 
exhaustive picture of the formation of GCs is yet to be reached.

The literature offers a wealth of formation scenarios. \citet{1968ApJ...154..891P}
and \citet{1984ApJ...277..470P} argue that GCs form as the earliest bound
structures in the Universe (i.e. prior to formation of the main galaxy), 
noting that the Jeans length and mass shortly after recombination is consistent
with typical GC masses and sizes. \citet{2005MNRAS.364..367D} and \citet{
2009ApJ...706L.192B} argue that the blue, metal-poor GCs ([Fe/H]$ < -1$) form in 
radially biased dark matter (DM) halos at high redshift. Other recent hypotheses 
of GC formation prior to collapse of the proto-galaxy include formation in colliding 
supershells \citep{2017Ap&SS.362..183R}, in supersonically induced gaseous objects
\citep{2019arXiv190408941C}, or in high-speed collisions of dark matter subhaloes
\citep{2019arXiv190508951M}. \citet{2017MNRAS.472.3120B} suggests
that (the blue subpopulation of) GCs could form in high density regions along
the cosmic filament before or during collapse.

@@

\newpage  % to prevent reference split over two pages which breaks LaTeX
Yet another hypothesis is that star cluster formation is triggered by major 
gas-rich (spiral) galaxy mergers \citep{1987nngp.proc...18S, 1992ApJ...384...50A},
which is naturally expected within the framework of hierarchical assembly. One
testable prediction of this scenario is the formation of young clusters in
interacting and merging galaxies, which has been observed and are found to show 
remarkable similarities with GCs in the Milky Way (MW) \citep[e.g.][]{
1995AJ....109..960W, 1996AJ....112..416H, 1999AJ....118..752Z, 1999AJ....118.1551W}.
Moreover, modelling efforts of this framework yield GC (sub)populations consistent 
with various observables \citep[e.g.][]{2010ApJ...718.1266M, 2018MNRAS.480.2343C}, 
and the recent numerical simulation of an isolated dwarf-dwarf merger executed at 
very high resolution (baryonic mass $m_b \sim$~4M\Sun; softening $\epsilon = 0.1$~pc) 
produces star clusters that could be GC progenitors \citep{
2019arXiv190509840L}.

@@

In this work we use state of the art simulations that produce realistic spiral 
galaxies (MW analogues) at redshift zero for which several global properties 
are consistent with the observations. The question thus naturally arises whether 
the star formation histories of the simulations give rise to a GCS similar to 
the MW and/or Andromeda (M31) GCSs. In particular, 
we use the Auriga simulations \citep[][hereafter G17]{2017MNRAS.467..179G}, 
further described in Section~\ref{sec:auriga}. We investigate whether the star 
formation model implemented produces metallicity, 
radial, and metallicity-radial distributions that are consistent with the MW 
and/or M31 GCSs, and whether the model produces enough stellar mass with
the right properties to allow for formation efficiencies lower than unity and
the expected (dynamical) mass loss over the cluster lifetime (not modelled 
explicitly in this study).

@@

\begin{figure}
    \includegraphics[width=\columnwidth]
        {{MW_RgcFeH_HistogramMassWeighted_Harris1996ed2010data-trim}.png}
    \centering \textcolor{lightgray}{\rule[2mm]{\columnwidth}{0.05mm}}
    \includegraphics[width=\columnwidth]
        {{M31_RgcFeH_HistogramMassWeighted_CaldwellRomanowsky2016data-trim}.png}
    \caption{
        \emph{Top}: Mass-weighted $r_{\text{gal}}$-[Fe/H] distribution of
        151 GCs in the MW \citep[data from][2010 ed.]{1996AJ....112.1487H},
        color-coded by the \textbf{median} (values also shown in each bin). The 
        numbers in parenthesis show how many star particles fall within the bin.
        \emph{Bottom}: Same for M31, showing the 366 GCs in CR16 
        \citep[data from][]{2016ApJ...824...42C}. Radii of M31 are again divided by 
        $r_{\text{vir,M31}}$ and multiplied by $r_{\text{vir,MW}}$. Note that the 
        range of the colourmap differs in both figures,
        \label{fig:observations_FeHRgc}
    }
\end{figure}

@@

\begin{figure}
    \includegraphics[width=0.49\textwidth]
        {{Au4-median_RgcFeH_HistogramMassWeighted_iold-trim}.png}
    \caption{
        Mass-weighted [Fe/H]-$r_{\text{gal}}$ distribution of all $30$~Auriga
        L4 haloes. Here we consider only the GC candidates and color-code by the 
        median mass (values also shown in each bin). The numbers in parenthesis 
        show how many star particles fall within the bin. Note that the range of 
        the colourmap differs from both panels in Figure~\ref{fig:observations_FeHRgc} 
        (for improved contrast within the plot).
        \label{fig:Au-FeHRgc}
    }
\end{figure}

@@

\begin{figure}
    \includegraphics[width=0.49\textwidth]
        {{Au4-median_RgcFeH_HistogramMassWeighted_MW_iold_diverging-trim}.png}
    \centering \textcolor{lightgray}{\rule[2mm]{\columnwidth}{0.05mm}}
    \includegraphics[width=0.49\textwidth]
        {{Au4-median_RgcFeH_HistogramMassWeighted_M31_iold_diverging-trim}.png}
    \caption{
        The top (bottom) panel shows the logarithm of the ratio of simulated mass
        to mass in the MW (M31) GCS, i.e. the logarithm of the mass ratio, minus
        the median value of these 25 bins. The values are 2.68 and 1.69 dex for 
        the MW and M31, respectively. Red (blue) indicates a higher (lower) overall 
        mass excess. The number in each bin shows the color-coded value that is 
        plotted, and the (median) star particle count is given in parenthesis. 
        Note that the three bins in the upper right corner are white because the 
        observations have zero mass there.
        \label{fig:Au-FeHRgc-ratio}
    }
\end{figure}

@@

We find that including more recently formed star particles in our subset 
of GC candidates shifts the mean metallicity to higher values. Moreover, the
total mass in metal-rich ([Fe/H] > -1) GC candidates increases for a lower age 
threshold and moves closer to the dotted line that shows the distribution of
all star particles in Figure~\ref{fig:FeH}. However, 
we notice that the Auriga simulations, on average, do not form new stars with 
a metallicity below [Fe/H]~=~-1 more recent than 6 Gyr ago: the behaviour of 
Figure~\ref{fig:FeH} does not change for metallicities below [Fe/H]~=~-1 when 
we change the age cut to 8 or 6 Gyr, and the slope of the masss ratio for 
metallicities above [Fe/H]~=~-1 is slightly steeper. In addition, we still find
that the accreted GC candidates are more metal-poor than those that have formed 
{\textit in situ}.

>>>>

\section{Introduction}
Globular star clusters (GC)s are old, bright, and ubiquitous. Various properties of
GC systems (GCS) show correlations with their host galaxies. GCSs are believed to
retain information about the galactic (gas) conditions at their times of formation.
Thus they could offer a unique insight into the (chemodynamical) evolution of their 
parent galaxies, if the formation and evolution of GCs- and GC systems themselves 
is adequately understood. However, despite decades of research (e.g.~\citealt{
1991ARA&A..29..543H, Harris2001, 2004Natur.427...31W, 2006ARA&A..44..193B, 
2012A&ARv..20...50G, 2014CQGra..31x4006K, 2018RSPSA.47470616F}), consensus on an 
exhaustive picture of the formation of GCs is yet to be reached. Most galaxies host
a GCS with a bimodal colour distribution that may reflect a bimodal metallicity 
distribution which is argued to arise from two distinct formation channels 
\citep{2006ARA&A..44..193B}. GCs are typically referred to as `blue' or `red' \citep[e.g.][]{
1985ApJ...293..424Z,1999AJ....118.1526G,2001AJ....121.2974L} where the former class
is more metal-poor, more radially extended, and showing little to no rotation wheras
the later is more metal-rich, radially concentrated, and rotating with the galaxy.

The literature offers a wealth of formation scenarios, many of which focus on the
distinct characteristics of the blue or red subpopulation. \citet{1968ApJ...154..891P}
and \citet{1984ApJ...277..470P} argue that GCs form as the earliest bound
structures in the Universe (i.e. prior to formation of the main galaxy), 
noting that the Jeans length and mass shortly after recombination is consistent
with typical GC masses and sizes. \citet{2005MNRAS.364..367D} and \citet{
2009ApJ...706L.192B} argue that the blue, metal-poor GCs ([Fe/H]$ < -1$) form in 
radially biased dark matter (DM) halos at high redshift. Other recent hypotheses 
of GC formation prior to collapse of the proto-galaxy include formation in colliding 
supershells \citep{2017Ap&SS.362..183R}, in supersonically induced gaseous objects
\citep{2019arXiv190408941C}, or in high-speed collisions of dark matter subhaloes
\citep{2019arXiv190508951M}. \citet{2017MNRAS.472.3120B} suggests
that (the blue subpopulation of) GCs could form in high density regions along
the cosmic filament before or during collapse.

@@

Yet another hypothesis is that star cluster formation is triggered by major 
gas-rich (spiral) galaxy mergers \citep{1987nngp.proc...18S, 1992ApJ...384...50A},
which is naturally expected within the framework of hierarchical assembly. One
testable prediction of this scenario is the formation of young clusters in
interacting and merging galaxies, which has been observed and are found to show 
remarkable similarities with GCs in the Milky Way (MW) \citep[e.g.][]{
1995AJ....109..960W, 1996AJ....112..416H, 1999AJ....118..752Z, 1999AJ....118.1551W}.
Moreover, modelling efforts of this framework yield GC (sub)populations consistent 
with various observables \citep[e.g.][]{2010ApJ...718.1266M, 2018MNRAS.480.2343C}, 
and the recent numerical simulation of an isolated dwarf-dwarf merger executed at 
very high resolution (baryonic mass $m_b \sim$~4M\Sun; softening $\epsilon = 0.1$~pc) 
produces star clusters that could be GC progenitors \citep{
2019arXiv190509840L}.

@@

In this work we use state of the art simulations that produce realistic spiral 
galaxies (MW analogues) at redshift zero for which several global properties 
are consistent with the observations. The question thus naturally arises whether 
the star formation histories of the simulations give rise to a GCS similar to 
the MW and/or Andromeda (M31) GCSs. In particular, 
we use the Auriga simulations \citep[][hereafter G17]{2017MNRAS.467..179G}, 
further described in Section~\ref{sec:auriga}. We investigate whether the star 
formation model implemented produces metallicity, radial, and metallicity-radial 
distributions that are consistent with the MW and/or M31 GCSs, and whether the 
model produces enough stellar mass with the right properties. Moreover, the simulations
provide us with the history of the star particles, which allows us to investigate
the differences between these properties for sub populations that have formed 
{\it in~situ} versus those that have been accreted. We focus on the metallicity
and radial distributions because observations of the red and blue GCs show
distinct differences between these properties.

@@

\begin{figure}
    \includegraphics[width=\columnwidth]
        {{MW_RgcFeH_HistogramMassWeighted_Harris1996ed2010data-trim}.png}
    \centering \textcolor{lightgray}{\rule[2mm]{\columnwidth}{0.05mm}}
    \includegraphics[width=\columnwidth]
        {{M31_RgcFeH_HistogramMassWeighted_CaldwellRomanowsky2016data-trim}.png}
    \caption{
        \emph{Top}: Mass-weighted $r_{\text{gal}}$-[Fe/H] distribution of
        151 GCs in the MW \citep[data from][2010 ed.]{1996AJ....112.1487H},
        colour-coded by the \textbf{median} (values also shown in each bin). The 
        numbers in parenthesis show how many star particles fall within the bin.
        \emph{Bottom}: Same for M31, showing the 366 GCs in CR16 
        \citep[data from][]{2016ApJ...824...42C}. Radii of M31 are again divided by 
        $r_{\text{vir,M31}}$ and multiplied by $r_{\text{vir,MW}}$. Note that the 
        range of the colourmap differs in both figures,
        \label{fig:observations_FeHRgc}
    }
\end{figure}

@@

\begin{figure}
    \includegraphics[width=0.49\textwidth]
        {{Au4-median_RgcFeH_HistogramMassWeighted_iold-trim}.png}
    \caption{
        Mass-weighted [Fe/H]-$r_{\text{gal}}$ distribution of all $30$~Auriga
        L4 haloes. Here we consider only the GC candidates and colour-code by the 
        median mass (values also shown in each bin). The numbers in parenthesis 
        show how many star particles fall within the bin. Note that the range of 
        the colourmap differs from both panels in Figure~\ref{fig:observations_FeHRgc} 
        (for improved contrast within the plot).
        \label{fig:Au-FeHRgc}
    }
\end{figure}

@@

\begin{figure}
    \includegraphics[width=0.49\textwidth]
        {{Au4-median_RgcFeH_HistogramMassWeighted_MW_iold_diverging-trim}.png}
    \centering \textcolor{lightgray}{\rule[2mm]{\columnwidth}{0.05mm}}
    \includegraphics[width=0.49\textwidth]
        {{Au4-median_RgcFeH_HistogramMassWeighted_M31_iold_diverging-trim}.png}
    \caption{
        The top (bottom) panel shows the logarithm of the ratio of simulated mass
        to mass in the MW (M31) GCS, i.e. the logarithm of the mass ratio, minus
        the median value of these 25 bins. The values are 2.68 and 1.69 dex for 
        the MW and M31, respectively. Red (blue) indicates a higher (lower) overall 
        mass excess. The number in each bin shows the colour-coded value that is 
        plotted, and the (median) star particle count is given in parenthesis. 
        Note that the three bins in the upper right corner are white because the 
        observations have zero mass there.
        \label{fig:Au-FeHRgc-ratio}
    }
\end{figure}

@@

We find that including more recently formed star particles in our subset 
of GC candidates shifts the mean metallicity to higher values. Moreover, the
total mass in metal-rich ([Fe/H] > -1) GC candidates increases for a lower age 
threshold and moves closer to the dotted line that shows the distribution of
all star particles in Figure~\ref{fig:FeH}. However, 
we notice that the Auriga simulations, on average, do not form new stars with 
a metallicity below [Fe/H]~=~-1 more recent than 6 Gyr ago: the behaviour of 
Figure~\ref{fig:FeH} does not change for metallicities below [Fe/H]~=~-1 when 
we change the age cut to 8 or 6 Gyr, and the slope of the masss ratio for 
metallicities above [Fe/H]~=~-1 is slightly steeper. In addition, we still find
that the accreted GC candidates are more metal-poor than those that have formed 
{\it in~situ}.
